---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-family: "Segoe UI", Arial, sans-serif;
  line-height: 1.6;
  margin: 20px;
  background-color: #EDBBE8;
}

h1 {
  color: #6A1B9A;
  font-weight: 700;
}

h2 {
  color: #6A1B9A;
  padding-bottom: 5px;
}

h3 {
  color: #6A1B9A;
}

p {
  font-size: 15px;
}

code {
  background-color: #f5f5f5;
  padding: 2px 4px;
  border-radius: 4px;
}

pre {
  background-color: #f5f5f5;
  padding: 10px;
  border-radius: 6px;
}

img {
  border-radius: 10px;
  margin-top: 10px;
}

```

## How Advertisement Format and Content Influence Engagement and Purchase Likelihood

This report analyses data collected from the Instagram Feed Advertisement Survey. 
The dataset includes information on advertisement format, number of likes, advertisement type, and user ratings.

The aim of this report is to investigate how different advertisement formats and types influence user engagement (likes) and purchase likelihood (ratings).  

```{r}

library(tidyverse)

# Initializing csv file
logged_data <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vRM2QXdIMKz0F1hPqLYh-YDABzuBbsQsFOEUljj28b-5RC-s9_O9v5aLgpTCSo_ebaXH_0BsDBiH9tn/pub?output=csv"

# Reading csv file, naming it "latest_data", and renaming variables/columns
latest_data <- read_csv(logged_data) %>%
  rename(timestamp = 1,
         ad_format = 2,
         ad_likes = 3,
         ad_type = 4,
         ad_rating = 5)

# The name of the most frequent value for ad format
latest_data$ad_format %>% 
  table() %>%
  which.max() %>%
  names() -> most_common_ad_format

# Splitting the ad type variable
data_type_split <- latest_data %>% 
  separate_rows(ad_type, sep = ",") %>%
  mutate(ad_type = str_trim(ad_type)) #Trims whitespace after splitting and overwrites data in the ad type column

# The name of the most frequent value for ad type (singular)
data_type_split$ad_type %>% 
  table() %>%
  which.max() %>%
  names() -> most_common_ad_type_singular

```

The average ad rating is **`r round(mean(latest_data$ad_rating, na.rm = TRUE), 1)`**.  
The most common ad format is **`r most_common_ad_format`**.  
The highest number of likes is **`r max(latest_data$ad_likes, na.rm = TRUE)`**.  
The most common content type is **`r most_common_ad_type_singular`**.

### Advertisement Format and Engagement

This graph shows the average number of likes for each advertisement format. This helps identify which formats generate the most engagement.


```{r}
# Plot #3: Bar graph of average likes of different ad formats
latest_data %>%
  group_by(ad_format) %>%
  summarise(avg_likes = mean(ad_likes)) %>%
  ggplot() +
  geom_col(aes(x = ad_format, y = avg_likes)) +
  labs(title = "Do different ad formats influence engagement?",
    subtitle = "Average number of likes by advertisement format from the Instagram Feed Advertisement Survey",
    x = "Advertisement Format",
    y = "Average Likes")
```


### Advertisement Type and Purchase Likelihood

This graph shows the average rating for each advertisement type. This indicates how likely I am/others are to purchase based on what is being advertised.


```{r, fig.width=12, fig.height=5}

# Plot #4: Bar graph of average rating of different ad types
data_type_split %>%
  group_by(ad_type) %>%
  summarise(avg_rating = mean(ad_rating)) %>%
  ggplot() +
  geom_col(aes(y = ad_type, x = avg_rating)) +
  labs(title = "Does product type influence purchase likelihood?",
    subtitle = "Average ratings by advertisement type from the Instagram Feed Advertisement Survey",
    x = "Average Rating",
    y = "Advertisement Type")

```


Overall, the results suggest that both advertisement format and content type play a role in influencing user engagement and purchase likelihood, although some categories perform significantly better than others.
